### 2022-03-21 rmd/suppl_info.Rmd
edit
Update suppl_info.Rmd

knitr::opts_chunk$set(echo = FALSE)

@@

  table_legend <- paste0("Sensitivity analysis of the ", c_text[i]," effect on the FCL. Parameter estimates of linear regression models are shown. Response variables are Spearman's rank correlation between food chain length and ", c_text[i],". Response and explanatory variables (i.e., simulation parameters) were standardized (mean = 0, SD = 1) before the analysis.")

@@

>>>>

knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE)

@@

  table_legend <- paste0("Sensitivity analysis of the ", c_text[i]," effect on the FCL. Parameter estimates of linear regression models are shown. The response variable is the Spearman's rank correlation between food chain length and ", c_text[i],". Response and explanatory variables (i.e., simulation parameters) were standardized (mean = 0, SD = 1) before the analysis.")

@@

\pagebreak

```{r si_figure_fcl}

source(here::here("code/figure_si_fcl.R"))

fig_fcl_chunk <- knit_chunk <- NULL

for(i in 1:length(list_g_fcl)) {

  figure_legend <- paste0(str_to_sentence(c_text[i])," effect on food chain length. We used the following values of parameters: $\\theta$ = `r df_sim$theta[i]`, $\\sigma_l$ = `r df_sim$sd_disturb_lon[i]`, and $\\sigma_h$ = `r df_sim$sd_disturb_source[i]`")

  knit_chunk <- paste0("## Figure S", i + j, " ", str_to_sentence(c_text[i]), " effect on food chain length", " \n",
                       "\n```{r figure_s", i + j,", fig.height = 6.5, fig.width = 8}
                       \n\n
                       list_g_fcl[[", i,"]]
                       \n\n
                       ```\n",
                       figure_legend,
                       "\n\\pagebreak\n")

  fig_fcl_chunk <- c(fig_fcl_chunk, knit_chunk)

`r paste(knit(text = fig_fcl_chunk), collapse = '\n')`
